Meta-analysis

### 2020-05-27 04_MetaAnalysis.Rmd
formating, description and MSE imputation description

imputed_error_list <- impute_yield_err(slimmer_PM_dat, "grain_yield.t.ha", "yield_error","n")

@@

The imputed variances calculated above don't show the expected positive correlation between grain yield and variance. This is unexpected and reflects the inherent variability of the data. Therefore we will calculate the trial mean squares and use this to calculate the variance for each sample.

@@

```{r imputing_MSE}
TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref)%>%
   summarise(unique(Y_Msquare))

TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
```

>>>>

imputed_error_list <- impute_yield_err(dat = slimmer_PM_dat, 
                                       xbar = "grain_yield.t.ha", 
                                       Var = "yield_error",
                                       reps = "n")

@@

The imputed variances calculated above don't show the expected positive correlation between grain yield and variance. This is unexpected and reflects the inherent variability of the data. Therefore we will equalise the variance by using the trial mean squares and use this to calculate the variance for each sample.

@@

```{r imputing_MSE}
TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref,location,year)%>%
   summarise(unique(Y_Msquare))

TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), c("trial_ref", "location","year")]
```
